Visual narratives of the Covid-19 pandemic

### 2022-01-24 JDSSV_manuscript_knitr.Rnw
Cleaning up files

%% new custom commands
\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}
\newcommand{\ma}[1]{\ensuremath{\mathbf{#1}}}

@@

download.file("https://www2.census.gov/programs-surveys/popest/tables/2010-2019/state/totals/nst-est2019-01.xlsx", destfile = "census_pop_state.xlsx", quiet = T, mode = "wb")
pop_data <- readxl::read_xlsx("census_pop_state.xlsx", col_names = c("state", "pop2019"), col_types = c("text", rep("skip", 11), "numeric"), skip = 9) %>%
  mutate(state = str_remove(state, "[[:punct:]]"))

@@

The Covid 19 pandemic has amply demonstrated that policies are only effectively implemented and followed by the population if they are accepted by a large majority of the population. To achieve this goal, effective communication of quantitative evidence and statistical results between scientists, governments, the media and citizens is essential to justify the appropriateness, usefulness and relevance of the measures.

>>>>

%% new custom commands
\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}
\newcommand{\ma}[1]{\ensuremath{\mathbf{#1}}}
\graphicspath{{Figures_R/}}
\graphicspath{{Figures_Web/}}

@@

download.file("https://www2.census.gov/programs-surveys/popest/tables/2010-2019/state/totals/nst-est2019-01.xlsx", destfile = "Data/census_pop_state.xlsx", quiet = T, mode = "wb")
pop_data <- readxl::read_xlsx("Data/census_pop_state.xlsx", col_names = c("state", "pop2019"), col_types = c("text", rep("skip", 11), "numeric"), skip = 9) %>%
  mutate(state = str_remove(state, "[[:punct:]]"))

@@

The Covid 19 pandemic has amply demonstrated that policies are only effectively implemented and followed by the population if they are accepted by a large majority of the population. To achieve this goal, it is essential that scientists, governments, the media, and citizens all effectively communicate in order to justify the appropriateness, usefulness and relevance of the measures. This is as true for guidelines about the use and creation of charts as it is for policies like masks and vaccines. % Making it a bit more explicit
